Python_basic

### 2022-11-03 Python_basic.qmd
Selenium Login and implicit wait

from selenium import webdriver
from selenium.webdriver.common.keys import Keys

@@

driver.find_element("xpath", '//*[@id="username"]').send_keys('tomsmith')
driver.find_element("xpath", '//*[@id="password"]').send_keys('SuperSecretPassword!')
driver.find_element("xpath", '//*[@id="login"]/button').click()

>>>>

from selenium import webdriver
from selenium.webdriver.common.keys import Keys
from selenium.webdriver.support.ui import WebDriverWait

@@

driver.find_element("xpath", '//*[@id="username"]').send_keys('tomsmith')
driver.find_element("xpath", '//*[@id="password"]').send_keys('SuperSecretPassword!')
driver.find_element("xpath", '//*[@id="login"]/button').click()
# driver.quit()

# Wait for response part
url02="https://the-internet.herokuapp.com/dynamic_loading/2"
driver.get(url02)
driver.find_element("xpath", '//*[@id="start"]/button').click()
driver.implicitly_wait(10)
text = driver.find_element("xpath", '//*[@id="finish"]/h4').text
print(text)
